### 2023-05-01 chapter2/chapter2.tex
Added chapter 2 abstract

\begin{abstract}
\noindent
Here's where my abstract will go!
\end{abstract}

>>>>

\begin{abstract}
\noindent
Intrinsically disordered regions (IDRs) are segments of proteins without stable three-dimensional structures. As this flexibility allows them to interact with diverse binding partners, IDRs play key roles in cell signaling and gene expression. Despite the prevalence and importance of IDRs in eukaryotic proteomes and various biological processes, associating them with specific molecular functions remains a significant challenge due to their high rates of sequence evolution. However, by comparing the observed values of various IDR-associated properties against those generated under a simulated model of evolution, a recent study found most IDRs across the entire yeast proteome contain conserved features. Furthermore, it showed clusters of IDRs with common ``evolutionary signatures,'' \textit{i.e.} patterns of conserved features, were associated with specific biological functions. To determine if similar patterns of conservation are found in the IDRs of other systems, in this work we apply a series of phylogenetic models to over 8,500 orthologous IDRs identified in the \textit{Drosophila} genome to dissect the forces driving their evolution. By comparing models of constrained and unconstrained continuous trait evolution, \textit{i.e.} the Brownian motion and Ornstein-Uhlenbeck models, we identify specific clusters of IDRs with shared patterns of constraint. As in yeast, these clusters are enriched for proteins with specific functional annotations, which suggests the preservation of distributed features and their associated functions is a widespread mechanism of IDR evolution.
\end{abstract}
